---
title: "Linear Regression Package"
author: "Sreenand.S and Fengjuanchen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Linear Model
Normal linear model
```{r setup}
library(ggplot2)
library(Lab04)
```
# Usage
```
linreg_mod <- linreg(formula, data)
```
## Arguments
-----------   ---------------------------------------------------------------------------------
__formula__   an object of class `"formula":` a symbolic description of the model structure to be                  fitted. The details of model specification are given under tram and in the package                 vignette.

__data__      an optional data frame, list or environment (or object coercible by `as.data.frame` to a data frame) containing the variables in the model. 

# Description
A Simple Linear model of a data frame.It estimates the regression coefficients of the given formula and also the residuals, degrees of freedom , the residual variance and the variance of the regression coefficients using the using the QR decomposition method.

The function returns an object of class s3 called linreg.

## Value
An object of class `Linreg`, with corresponding `coef`, `coefvariance`, `qr_coef`, `estfun`, `summary`, `print`, `plot`,`residualvariance` and `df`.

## Example



### QR decomposition function
```{r}
linreg_mod<-linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
coef(linreg_mod)
```

### Print function
```{r}
linreg_mod <- linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
print(linreg_mod)
```

### Summary function
```{r}
linreg_mod <- linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
summary(linreg_mod)
```

### lm Summary function
```{r}
linreg_mod <- lm(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
summary(linreg_mod)
```




